Hydraulically-vulnerable trees survive on deep-water access during droughts in a tropical forest

### 2021-02-18 10.0_Supporting_Information.Rmd

```{r, include=FALSE, echo = FALSE}
if(!require("pacman", quietly=TRUE)) install.packages("pacman")
suppressPackageStartupMessages(
  pacman::p_load(bookdown, knitr, pander, citr, broom))
options(tinytex.verbose = TRUE)
source("code/07.0_load.R")
source("code/08.0_manuscript_data_figs.R")
# load("results/manuWorkSpace.RData")
# install.packages(c("vctrs", "rlang"))
```

>>>>

```{r, include=FALSE, echo = FALSE}
if(!require("pacman", quietly=TRUE)) install.packages("pacman")
suppressPackageStartupMessages(
  pacman::p_load(bookdown, knitr, pander, citr, broom))
options(tinytex.verbose = TRUE)
source("code/06.0_load.R")
source("code/08.0_manuscript_data_figs.R")
# load("results/manuWorkSpace.RData")
# install.packages(c("vctrs", "rlang"))
```
